\documentclass{article}
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage[none]{hyphenat}
\usepackage[xetex,
        pdftitle={Brendan Coffey's Resume},
        pdfauthor={Brendan M. Coffey},
        colorlinks=true,
        urlcolor=blue,
        filecolor=green,
        linkcolor=blue,
        pdfproducer={xetex},
        pagebackref,
        pdfpagemode=None,
        bookmarks=true,
        bookmarksopen=true]{hyperref}

\textheight=9.0in
\setlength{\tabcolsep}{0in}
\def\arraystretch{1.5}

\definecolor{mydarkgrey}{gray}{.1}
\definecolor{mygrey}{gray}{.85}

\newcommand{\resheading}[1]{\section*{#1}}

\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0em}

\begin{document}

\hyphenation{Open-LDAP}

\author{Brendan M. Coffey}

\textbf{\LARGE Brendan M. Coffey}\\
Los Angeles, California, USA \\
bmc+resume@section9.net

\resheading{Objective}

I want to work with a talented, passionate team to improve humanity's circumstances. I have broad technical experience in areas from embedded systems and signal processing to application software and team management. I enjoy collaborating on creative solutions to difficult problems.

\resheading{Professional Skills}

\begin{tabular}{l p{5in}}
    
    \underline{\smash{Programming:}} & C/C++/boost, Python, Java, C\#/.NET, Javascript, gcc, gdb, Intel icc \& VTune, JTAG debugging, CUDA, OpenCL, Microsoft Accelerator\\
    
    \underline{\smash{Frameworks / Tools:}} & Vim, Visual Studio, SublimeText, git, subversion, gstreamer, Matlab, Apache, NGINX, MySQL, node.js, Kafka, Zookeeper, Hadoop, Hive \\
    
    \underline{\smash{OS \& Platforms:}} & Linux, OS X, FreeBSD, Windows, ARM, Raspberry Pi, Pixhawk\\
    
\end{tabular}

\resheading{Professional Experience}

{\bf Senior Software Engineer,} \href{http://www.ecofactor.com/}{Ecofactor} \hfill March 2013 -- September 2015

\begin{itemize} \itemsep -2pt  % reduce space between items
    
    \item As a senior member of the platform, data science, and application teams, enabled municipal and regional power utilities to manage and shape residential electrical demand.
    
    \item Built data collection, analysis, and customer-facing systems, for provisioning and management of Internet-connected smart thermostats.
    
    \item Built simulation and test infrastructure to allow the engineering team to scale-test our system into the millions of connected devices.
    
    \item Redesigned the company's core data aggregation and analytics system.
    
    \item Implemented features and performance/usability optimizations in iOS/Android customer app using Cordova/PhoneGap.
    
\end{itemize}

{\bf Senior Software Engineer,} Portfolio Analytics, \href{https://www.thomsonreuters.com}{Thomson Reuters}\hfill January 2012 -- March 2013
\begin{itemize} \itemsep -2pt
    
    \item Architected, designed and implemented systems supporting portfolio performance analytics and risk modeling.
    
    \item Lead architecture and implementation of custom, generic C\# class library for manipulation of time-series financial data.
    
    \item Prototyped optimization of large matrix computations using Microsoft Accelerator on NVidia GPUs.
    
    \item Lead development of devops and deployment infrastructure for multi-tier .NET applications in C#.
    
\end{itemize}

{\bf Software Engineer,} Primary Analysis, \href{http://www.pacb.com/}{Pacific Biosciences}\hfill September 2009 -- September 2011
\begin{itemize} \itemsep -2pt
    
	\item Implemented image processing and signal extraction system to process 25 GB/s of video data in real time.
    
    \item Designed and wrote a module for real time visual display of extracted signal data.
    
	\item Designed and implemented distributed computation system for on-instrument data analysis.
	
	\item Investigated and benchmarked use of NVidia GPUs for signal processing to increase system multiplex and throughput.
    
\end{itemize}

{\bf Instrument Software Engineer,} \href{http://www.pacb.com/}{Pacific Biosciences}\hfill November 2007 -- September 2009
\begin{itemize} \itemsep -2pt
    
	\item As a core R\&D software engineer, designed and built control and management software for a single-molecule, real-time genetic sequencing machine.
	
	\item Collaborated with chip manufacturing engineers to develop work flow for automated evaluation and acceptance testing of imaging microchips. (Python)
    
    \item Designed and wrote an execution engine to run user-editable experiment protocols generated by internal and external customers.
    
    \item Lead development of manufacturing acceptance tests for data acquisition and signal processing software systems.
    
\end{itemize}

{\bf Software Engineer,} \href{http://www.aplix.co.jp/en/}{Aplix Corporation}\hfill 2005 -- 2007
\begin{itemize} \itemsep -2pt
    
	\item As a software engineer on the core Java virtual machine, worked with a team specifying and implementing the Mobile Information Device Profile (MIDP) 3.0 for cellphone handsets.
	
	\item Supported customer companies' engineers in resolving system bugs and performance problems.
	
	\item Cooperated with partner company's engineering group for JVM bring-up on a new platform architecture.
    
\end{itemize}

{\bf Director of Information Technology,} The Orphanage, Inc. \hfill 2003 -- 2005
\begin{itemize} \itemsep -2pt

	\item As both a senior systems programmer and then the Director of Information Technology, took responsibility for all IT resources and operations of a medium-sized digital special effects, feature-film and commercial post-production company.
	
	\item Managed a team of 25 systems, software development, and technical support staff supporting all functions of the organization.
    
	\item Built a custom business intelligence, resource and IT tracking system for a facility of 200 artists, producers and supervisory staff. The system tracked usage of all IT resources, employee time tracking, and provided data and analysis to support executive decision-making.

\end{itemize}

\resheading{Interests \& Hobbies}

    \begin{itemize}\itemsep -2pt
        \item Avid scuba diver. \href{https://www.padi.com/}{PADI} certified Divemaster No. 381509 (April 2016)
        \item Expert backpacker, skier \& back-country traveler.\newline
        Member of \href{https://americanalpineclub.org/}{American Alpine Club} and \href{www.sierramountaineeringclub.org}{Sierra Mountaineering Club}.
        \item Drone robotics hobbyist. Built \href{http://bluerobotics.com/}{Blue Robotics} \href{https://github.com/leetbmc/bluerov}{BlueROV 1}. (Fall 2016)
    \end{itemize}

\resheading{Education}
   \href{https://www.northeastern.edu/}{Northeastern University}, Boston, Massachusetts \hfill 1997-2001\\
   Degree: Bachelor of Science in Computer Science \& Applied Mathematics\\

\end{document}
