\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[top=0.75in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}

\name{Brendan}{Coffey}
\title{Principal Architect, Data Systems}
\address{Pasadena, CA}{}{}
\phone[mobile]{+1~(408)~205~0031}
\email{bmc+resume@section9.net}
\homepage{linkedin.com/in/brendancoffey}

\begin{document}
\makecvtitle

\section{Summary}
Dynamic, hands-on software engineer and technical leader, with 20+ years designing embedded and distributed systems, data platforms, applications and infrastructure. I build happy teams of productive engineers. I thrive in production, product-oriented environments, where systems and software must be reliable. Deep, multidisciplinary engineering experience allows me to bring creative problem solving and leadership to complex technical and business challenges.

\section{Experience}

\cventry{2020--Present}{Senior Principal Architect, Data Systems}{Equinix}{Remote / Los Angeles, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Founded, hired, and lead 10-person data platform team. Hired manager, software and devops engineers; coached and trained platform engineers in software design and development.
  \item Lead platform architecture in Google Cloud for data systems used by ~5,000 enterprise analytics and ML/AI users.
  \item Responsible for capacity planning and resource management, including vendor contract and commit negotiations.
  \item Evolved team from IT/back-office model to 24x7 SLA, to support customer and ops facing data applications.
  \item Designed and implemented test automation framework for data pipelines.
\end{itemize}
\end{minipage}}

\cventry{2017--2020}{Director, Data Engineering}{The Walt Disney Studios}{Burbank, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Founded and scaled a 6-person data platform engineering team.
  \item Oversaw architecture, roadmap, hiring, budgeting, and vendor management.
  \item Reduced ~70 person data engineering and analytics team to under 30, while expanding services to include self-service data exploration, visualization, and machine learning facilities.
  \item Supervised the design and implementation of data platform services, including Spark, Airflow, and data governance tools.
  \item Negotiated and signed vendor master service agreement with Databricks on behalf of Walt Disney Company.
  \item Hired and led team to build the Studio's first machine-learning-based box office projection model.
\end{itemize}
\end{minipage}}

\cventry{2013--2015}{Senior Software Engineer}{EcoFactor}{Redwood City, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Architected and implemented distributed control, data collection and analytics systems for residential smart thermostats.
  \item Designed and implemented core data collection, aggregation, analytics, and control messaging.
  \item Built an event-driven simulator in Node.js to for platform scaling simulations from O(10K) to O(10M) devices.
\end{itemize}
\end{minipage}}

\cventry{2012--2013}{Senior Software Engineer}{Thomson Reuters}{San Francisco, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Developed risk and portfolio analytics infrastructure in .NET and C\#.
  \item Designed high-performance matrix computation and caching systems.
  \item Led devops tooling and deployment automation for multi-tier apps.
\end{itemize}
\end{minipage}}

\cventry{2007--2011}{Software Engineer}{Pacific Biosciences}{Menlo Park, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Distributed systems and control software for real-time DNA sequencing instruments.
  \item Implemented soft real-time control and infrastructure for instrument bring-up.
  \item Designed and implemented primary signal acquisition system, including calibration and realtime image processing.
\end{itemize}
\end{minipage}}

\iffalse

\cventry{2005--2007}{Software Engineer}{Aplix Corporation of America}{}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Contributed to Java Virtual Machine (JVM) and MIDP 3.0 implementation for mobile platforms.
  \item Delivered Java VM tech to Motorola, Nokia, and Symbian device lines.
\end{itemize}
\end{minipage}}

\cventry{2005--2006}{Director of IT}{The Orphanage}{San Francisco, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Led all IT operations for a digital VFX studio; managed 25-person technical team.
  \item Oversaw systems, networking, infrastructure, and internal software dev.
\end{itemize}
\end{minipage}}

\cventry{2004--2005}{Software Engineer}{The Orphanage}{San Francisco, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Built custom IT, HR, and project tracking systems for resource use and financial reporting.
  \item Supported digital VFX workflow for 180+ artists and supervisors.
\end{itemize}
\end{minipage}}

\cventry{2003--2004}{Software Engineer}{Wavemarket}{}{}{}

\cventry{2001--2002}{Software Engineer}{Voom, Inc.}{}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Delivered software solutions and consulting for ASIC and FPGA development projects.
\end{itemize}
\end{minipage}}

\fi

\section{Education}
\cventry{}{B.S. Computer Science \& Applied Mathematics}{Northeastern University}{Boston, MA}{}{
Activities: Student Systems Group, Hiking \& Outing Club}

\iffalse

\section{Technical Skills}
\cvitem{Languages}{Python, Java, Scala, Go, C\#, SQL}
\cvitem{Cloud}{GCP (BigQuery, Dataflow, Dataproc, Composer), AWS}
\cvitem{Data}{Airflow, Spark, Kafka, Hadoop, Beam, Looker, Amundsen, DBT}
\cvitem{MLOps}{Vertex AI, TensorFlow, ML pipeline orchestration}
\cvitem{DevOps}{Docker, Kubernetes, Terraform, GitHub Actions, Prometheus}

\section{Community}
\cvitem{Speaking}{O’Reilly AI Conf, Google Cloud Next, local engineering meetups}
\cvitem{Open Source}{Apache Beam, dbt-labs contributor}

\fi

\end{document}

