
\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[top=0.75in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}

\name{Brendan}{Coffey}
\title{Principal Architect, Data Systems}
\address{Redwood City, CA}{}{}
\phone[mobile]{+1~(555)~555~5555}
\email{brendan.coffey@email.com}
\homepage{linkedin.com/in/brendancoffey}
\social[github]{brendancoffey}

\begin{document}
\makecvtitle

\section{Summary}
Architect and engineering leader with 20+ years designing distributed systems, data platforms, and infrastructure. Deep hands-on experience in cloud-native systems, analytics, and machine learning enablement.

\section{Experience}

\cventry{2020--Present}{Senior Principal Architect, Data Systems}{Equinix}{Remote / Los Angeles, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Lead platform architecture for data systems used by ~5,000 enterprise analytics and ML users.
  \item Directed 10-person platform team; coached and trained a 70-member data engineering org.
  \item Built hybrid GCP/on-prem platform using BigQuery, Dataflow, and Cloud Composer.
\end{itemize}
\end{minipage}}

\cventry{2017--2020}{Senior Manager, Data Engineering}{The Walt Disney Studios}{Burbank, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Founded and scaled a 15-person platform engineering team at Disney Studios.
  \item Rebuilt ingest, processing, and reporting platform using Spark, Airflow, Kubernetes, Amundsen.
  \item Oversaw roadmap, hiring, budgeting, vendor management, and architecture decisions.
\end{itemize}
\end{minipage}}

\cventry{2017}{Consulting Software Engineer}{The Walt Disney Studios}{Burbank, CA}{}{}

\cventry{2013--2015}{Senior Software Engineer}{EcoFactor}{Redwood City, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Architected and implemented distributed control and analytics systems for smart thermostats.
  \item Built large-scale event simulators in Node.js to stress-test platform.
  \item Rewrote core data aggregation systems in Python/Hadoop and built distributed messaging with Java, Kafka, Zookeeper, Flume.
\end{itemize}
\end{minipage}}

\cventry{2012--2013}{Senior Software Engineer}{Thomson Reuters}{San Francisco Bay Area}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Developed risk and portfolio analytics infrastructure in .NET and C#.
  \item Designed high-performance matrix computation and caching systems.
  \item Led devops tooling and deployment automation for multi-tier apps.
\end{itemize}
\end{minipage}}

\cventry{2007--2011}{Instrument Software Engineer}{Pacific Biosciences}{Menlo Park, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Designed distributed systems and control software for real-time DNA sequencing instruments.
  \item Implemented soft real-time systems and infrastructure for instrument bring-up.
\end{itemize}
\end{minipage}}

\cventry{2005--2007}{Software Engineer}{Aplix Corporation of America}{}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Contributed to Java Virtual Machine (JVM) and MIDP 3.0 implementation for mobile platforms.
  \item Delivered Java VM tech to Motorola, Nokia, and Symbian device lines.
\end{itemize}
\end{minipage}}

\cventry{2005--2006}{Director of IT}{The Orphanage}{San Francisco, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Led all IT operations for a digital VFX studio; managed 25-person technical team.
  \item Oversaw systems, networking, infrastructure, and internal software dev.
\end{itemize}
\end{minipage}}

\cventry{2004--2005}{Software Engineer}{The Orphanage}{San Francisco, CA}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Built custom IT, HR, and project tracking systems for resource use and financial reporting.
  \item Supported digital VFX workflow for 180+ artists and supervisors.
\end{itemize}
\end{minipage}}

\cventry{2003--2004}{Software Engineer}{Wavemarket}{}{}{}

\cventry{2001--2002}{Software Engineer}{Voom, Inc.}{}{}{\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item Delivered software solutions and consulting for ASIC and FPGA development projects.
\end{itemize}
\end{minipage}}

\section{Education}
\cventry{1997--2001}{B.S. Computer Science \& Applied Mathematics}{Northeastern University}{Boston, MA}{}{
Activities: Student Systems Group, Hiking \& Outing Club}

\section{Technical Skills}
\cvitem{Languages}{Python, Java, Scala, Go, C\#, SQL}
\cvitem{Cloud}{GCP (BigQuery, Dataflow, Dataproc, Composer), AWS}
\cvitem{Data}{Airflow, Spark, Kafka, Hadoop, Beam, Looker, Amundsen, DBT}
\cvitem{MLOps}{Vertex AI, TensorFlow, ML pipeline orchestration}
\cvitem{DevOps}{Docker, Kubernetes, Terraform, GitHub Actions, Prometheus}

\section{Certifications}
\cvitem{2023}{Google Cloud Professional Data Engineer}
\cvitem{2022}{Certified Kubernetes Administrator (CKA)}

\section{Community}
\cvitem{Speaking}{O’Reilly AI Conf, Google Cloud Next, local engineering meetups}
\cvitem{Open Source}{Apache Beam, dbt-labs contributor}

\end{document}
